\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{hyperref}

\title{How can the Santa Ana sucker be saved?}
\author{Marc Los Huertos}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\maketitle

\section{Introduction}

According to Kolbert 201X, we are in the midst of a dramatic extinction event -- rivaling major catostrophic extinctions in the past. The difference with the current situation is the cause: The dominance of human beings over the Earth's surface led to the extirpation of thousands of species, and counting. 

It's easy to second guess various scienctific and policy questions with respect to endangered species, but when we begin to evaluate what is actually being done on the ground for various species, we quickly learn that we are not just in a ecological web, we are also in a policy and regulatory morass. 

\subsection{Driving Question}

This project will attempt to answer the following question, "How can we save the Santa Ana sucker?" As we have seen, this is a generic question that needs to be constrained, defined, and subject to what we already know about the sucker. In addition, we need to define the terms used in the question, such as who is "we"? What do we mean by "save"?  And finally, when we ask "how", what are the options avaible that might fit into the "how"?  

\section{Learing Goals}

\begin{itemize}
  \item Evaluate sucker habitat using the following tools:
  \begin{itemize}
    \item Define Water Quality Goals
    \item Characterize Hydrology and Geomophology
    \item Analyze Community Profile of Periphyton
  \end{itemize}
  \item Propose and evaluate options to improve Santa Ana sucker habitat.
  \item Prepare sets of pratical and effective measures that might protect (or increase) the extant populations of the Santa Ana sucker.
\end{itemize}

\subsection{Why these learning goals?}

\section{Project Stages}

\begin{itemize}
  \item Session 1: Define 'Public Product'
  \item Session 2: Revise 'Driving Question' and list resources needed
\end{itemize}

\section{Defining the Public Product}

For this project, each student will contribet to one of four briefs on the science available to "resore and protect" the Santa Ana Sucker. 

Although the audience will be the public... the breifs will be submitted the the USFWS the the USFWS and City of San Bernardino... etc...??

Each "issue" of the research briefs, will address a different scientific issues associated with the Santa Ana sucker--where each issues addresses a specific driving question with respect to the sucker. 
EA 30 Research Briefs are short (3-4 pages) descriptions of recently EA30 project results. These "briefs" highlights also include one image, a caption (50 words), and several publication citations. Each student scientists are invited to develop one to several breifs that will be made available to the public.

Teams will be in charge of each issue, but each student will make an individual contribution. The group will decide how to arrange the order of each individual based on the quality and potential interests for each of the sections.  

\begin{description}
  \item[Issue 1: Habitat Loss] 
  \item[Issue 2: Food Quality] 
  \item[Issue 3: Water Quality]
  \item[Issue 4: Hydrology]
  \item[Issue X: Geomorphology]
\end{description}

\subsection{Examples}

\href{https://www.fws.gov/Endangered/esa-library/index.html}{https://www.fws.gov/Endangered/esa-library/index.html}

\href{http://blogs.scientificamerican.com/extinction-countdown/}{http://blogs.scientificamerican.com/extinction-countdown/}

\subsection{Evaluation Criteria of Public Products}

\section{Driving Question}

\subsection{Define and constrain driving question}

As one of our first excercises, we will explore the meaning of the driving question. As we work to understand our driving question, we will create groups of students to act as research teams that will address a portion of the driving question.

\subsection{Resources to answer driving question}

Each team will determine what resources are avaialble and/or needed to address the driving question. Working with the instructor is key because these resources need to be made available for the following week.

\subsection{Determine Required Resources and Methods}


\subsection{Answering the Driving Questions}

\subsection{Data Collection and Analysis}

\section{Create Public Product}

\subsection{Writing and Presenting Results}

\end{document}
