\documentclass{article}

\title{5-Day Biochemical Oxygen Demand Test (BOD5)}
\author{Leah Ho-Israel}

\usepackage{Sweave}
\begin{document}
\input{BOD5_Methods-concordance}

\maketitle

\section*{Preparation of Reagents}
\begin{enumerate}
  \item \emph{Phosphate Buffer}--Dissolve 8.5 g KH2PO4, 21.75 g K2HPO4, 33.4 g Na2HPO4*7H2O, and 1.7 g NH4Cl in ~500 mL distilled water. Stirring and/or heating may be required. Dilute to 1 L.
  
  \item \emph{Magnesium sulfate solution}--Dissolve 4.5 g MgSO4*7H2O in distilled water, dilute to 200 mL. 
  
  \item \emph{Calcium chloride solution}--Dissolve 5.5 g CaCl2 in distilled water, dilute to 200 mL.
  
  \item \emph{Ferric chloride solution}--Dissolve 0.05 g FeCl3*6H2O in distilled water, dilute to 200 mL. 
  \item \emph{Sodium sulfite solution}--Dissolve 1.575 g Na2SO3 in 1000 mL distilled water. 
\subitem **Not stable so prepare daily.
  \item \emph{Glucose-glutamic acid solution}--Add 150 mg of pre-dried glucose and 150 mg of pre-dried glutamic acid to distilled water, dilute to 1 L. 
  \subitem **Prepare immediately before use, unless maintained in sterile condition.
  \subitem **Store mixtures at 4 degrees C or lower. 
  \item \emph{Ammonium chloride solution}--Dissolve 1.15 g NH4Cl in ~500 mL distilled water and adjust pH to 7.2 using NaOH solution. Dilute to 1 L. 
  \item \emph{Allylthiourea (ATU) solution}--Dissolve 2.0 g C4H8N2S in ~500 mL distilled water, dilute to 1 L. 
  \subitem **Store at 4 degrees C.
  \subitem **Not stable for more than 2 weeks. 
  \item \emph{Seed suspension}--Dissolve the contents of 5 capsules of PolySeed in 2500 mL 
\end{enumerate}

\section*{Preparation of Samples}
\begin{enumerate}
  \item Transfer 25, 50, and 100 mL of sample water from each site to 300 mL glass incubation bottles. 
\end{enumerate}

\end{document}
