\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\section{Data Description}

This data was collected on September 20, 2016 along 3 reaches of the Santa Ana River, with 9 observations per reach. Each observation contains the following variables:  

\subsection{Importing Data}


\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{file} \hlkwb{=} \hlstr{"/home/CAMPUS/mwl04747/github/Santa-Ana-Sucker-Recovery/Data/Data_TUES_1/AllParameters.csv"}
\hlstd{import} \hlkwb{<-} \hlkwd{read.csv}\hlstd{(file)}
\end{alltt}
\end{kframe}
\end{knitrout}


\subsection{Summary Statistics}


 

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{summary}\hlstd{(import)}
\end{alltt}
\begin{verbatim}
##  Site      Algae           Sediment       Temperature        Canopy      
##  A:9   Min.   :  0.00   Min.   :0.0000   Min.   :28.00   Min.   : 0.000  
##  B:9   1st Qu.:  0.00   1st Qu.:0.0000   1st Qu.:29.00   1st Qu.: 3.000  
##  C:9   Median : 50.00   Median :1.0000   Median :29.00   Median :11.000  
##        Mean   : 48.52   Mean   :0.5926   Mean   :28.89   Mean   : 8.593  
##        3rd Qu.:100.00   3rd Qu.:1.0000   3rd Qu.:29.00   3rd Qu.:14.000  
##        Max.   :100.00   Max.   :1.0000   Max.   :30.00   Max.   :15.000
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsection{Distribution}

Write some stuff about the summary here...
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{hist}\hlstd{(import}\hlopt{$}\hlstd{Predictor)}
\end{alltt}


{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in hist.default(import\$Predictor): 'x' must be numeric}}\end{kframe}
\end{knitrout}

ANOVA TESTS summary(results.aov)

Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1           

Algae v Site: 
Pr(>F)     7.19e-08 ***
         HIGHLY SIGNIFICANT          
---
 v Sediment
           Pr(>F)  
Sediment   0.0643 . 
          SIGNIFICANT
               
---
v Temperature
  
             Pr(>F)
Temperature  0.446
             NOT SIGNIFICANT
----
Canopy 

       Pr(>F)
Canopy 0.334
            NOT SIG.
           SHOULD DO REGRESSION INSTEAD?

---
Algae~Site+Temperature
  
            Pr(>F)    
Site        2.53e-07 ***
Temperature 0.0714 .  
           SIG. 
           SHOULD DO REGRESSION INSTEAD?
---
Algae~Site+Sediment

            Pr(>F)    
Site       4.73e-07 ***
Sediment   0.211    

          HIGHLY SIGNIFICANT (2nd in significance?)
                   
---
Algae~Site+Sediment+Temperature

Df Sum Sq Mean Sq F value   Pr(>F)    
Site         2.95e-07 ***
Sediment     0.1918    
Temperature  0.0858 .  
                MIXING CATEGORICAL AND CONT. PREDICTORS. 
                NEED OTHER TEST?
---
Algae~Site+Sediment+Temperature+Canopy
   
             Pr(>F)    
Site         5.43e-07 ***
Sediment     0.2004    
Temperature  0.0919   .  
Canopy       0.6591  

MIXING CATEGORICAL AND CONT. PREDICTORS. 
                NEED OTHER TEST?
                   
---
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{hist}\hlstd{(import}\hlopt{$}\hlstd{Response)}
\end{alltt}


{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in hist.default(import\$Response): 'x' must be numeric}}\end{kframe}
\end{knitrout}

\section{Bias and Data Limitations}

All data collected on one day, Sept. 20, 2016.

Abnormal event (car accident) occurred a few ? days before data collection which caused the RIX treatment plant to temporarily shut off water outlet pipes, effectively draining the river and adeversely impacting algae populations to an unknown degree. Therefore our measurements likely reflect less-than-typical algae abundance. Our measuremnts were taken by undergraduate students without extensive algae fieldwork experience or training. 


\end{document}
